\huge \textbf{Parameter Forecasts From CMB Lensing and Galaxy Lensing Power- and Bispectra}

### 2025-05-06 paper/paper_draft.tex
paper changes

\begin{figure}
    \centering
    \tiny
    \begin{tabular}{lrrrrr}
        \hline
         Par            &   CMB + Gal Powersp &   CMB + Gal Bisp &   CMB Power- + Bisp &   Gal Power- + Bisp &   CMB + Gal Power- + Bisp \\
        \hline
         $H_0$          &                41.0 &              1.9 &                 7.4 &                 4.8 &                       0.7 \\
         $\Omega_b h^2$ &               109.8 &             18.4 &                10.1 &                17.3 &                       7.1 \\
         $\Omega_c h^2$ &                58.3 &              2.4 &                 2.2 &                 2.7 &                       1.1 \\
         $n_s$          &                11.4 &              1.9 &                 1.8 &                 3.2 &                       1.0 \\
         $m_\nu$        &               603.3 &            373.9 &               216.3 &               260.1 &                     102.3 \\
         $A_s$          &                39.1 &              7.0 &                 3.4 &                 7.8 &                       2.4 \\
         $w_0$          &                46.1 &              3.1 &                18.3 &                12.7 &                       1.6 \\
        \hline
    \end{tabular}
\caption{Parameter constraints in percentage of the fiducial values for different combinations of weak lensing information.}
\label{tab:paramconstraintsall}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/param_constraints_all.pdf}
    \caption{Same as Fig. \ref{fig:paramconstraintstight}, except comparing constraints for all parameters of our $\Lambda$CDM cosmology.}
    \label{fig:paramconstraintsall}
\end{figure}

\begin{figure}
    \centering
    \tiny
    \begin{tabular}{lrrrrr}
        \hline
         Par        &   CMB + Gal Powersp &   CMB + Gal Bisp &   CMB Power- + Bisp &   Gal Power- + Bisp &   CMB + Gal Power- + Bisp \\
        \hline
         $H_0$      &        3.3022621043 &     0.9658765234 &        0.1360204496 &        0.6433515918 &              0.1173950908 \\
         $\sigma_8$ &        0.0000000178 &     0.0000000148 &        0.0000000023 &        0.0000000122 &              0.0000000020 \\
         $\Omega_m$ &        0.4126866976 &     0.2388283763 &        0.1579156300 &        0.1996632391 &              0.1122269336 \\
        \hline
    \end{tabular}
\caption{Same as table \ref{tab:paramconstraintsall}, except for a smaller selection of parameters well constrained by lensing.}
\label{tab:paramconstraintstight}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/param_constraints_tight.pdf}
    \caption{Constraints for $H_0$, $\sigma_8$, and $\Omega_m$ for different combinations of weak lensing spectra. Valid for ``stage 4'' experiments. We use $l_{\max}=2000$. The confidence ellipses are for $1\sigma$ certainty. The standard deviation of each Gaussian is given explicitly in the top left corners of the diagonal plots.}
    \label{fig:paramconstraintstight}
\end{figure}

@@

\pagebreak
\printbibliography

@@

\begin{table}[h]
    \centering
    \begin{tabular}{lcc}
    \toprule
    Parameter & Fiducial value & Finite difference ($h$) \\
    \midrule
    $H$            & $67.4$               & fiducial\,$\times0.1$   \\
    $\Omega_b h^2$ & $0.0223$             & fiducial\,$\times0.1$   \\
    $\Omega_c h^2$ & $0.119$              & fiducial\,$\times0.005$ \\
    $n_s$          & $0.965$              & fiducial\,$\times0.005$ \\
    $A_s$          & $2.13\times10^{-9}$  & fiducial\,$\times0.1$   \\
    $m_\nu$        & $0.06$               & fiducial\,$\times0.1$   \\
    $w_0$          & $-1$                 & $0.03$                  \\
    \bottomrule
    \end{tabular}
    \caption{Fiducial cosmological parameters and their finite-difference steps}
    \label{tab:cosmo-params-diff}
\end{table}

>>>>

\begin{figure}
    \centering
    \tiny
    \begin{tabular}{lrrrrr}
        \hline
         Par            &   CMB + Gal Powersp &   CMB + Gal Bisp &   CMB Power- + Bisp &   Gal Power- + Bisp &   CMB + Gal Power- + Bisp \\
        \hline
         $H_0$          &        9.8607392131 &     1.9228760331 &        5.0596593228 &        4.9998059321 &              0.6566865031 \\
         $\Omega_b h^2$ &       21.1047938757 &    22.3422408475 &        9.9278715395 &       19.0626128005 &              6.6783756779 \\
         $\Omega_c h^2$ &        0.0000125702 &     1.9971113528 &        0.0000125243 &        2.4722397353 &              0.0000125239 \\
         $n_s$          &        2.5555063255 &     2.0884251995 &        1.0353938531 &        3.4233966612 &              0.6771684184 \\
         $m_\nu$        &      540.3486045452 &   397.7301866598 &      197.9074769610 &      274.0779514021 &            110.8336892534 \\
         $A_s$          &       17.8092869822 &     7.5399323519 &        4.1275268227 &        7.9422103452 &              2.0233577134 \\
         $w_0$          &       43.5247638551 &     3.8394789067 &       12.3789001621 &       13.7550208605 &              1.7287298348 \\
        \hline
        \end{tabular}
\caption{Parameter constraints in percentage of the fiducial values for different combinations of weak lensing information.}
\label{tab:paramconstraintsall}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/param_constraints_all.pdf}
    \caption{Parameter constraints and confidence ellipses for $\Lambda$CDM model as well as neutrino mass and dark energy equation of state parameter. Using ``stage 4'' noise with multipole range from $2$ to $2000$. Different weak lensing information combinations considered. No priors used. The confidence ellipses are for $1\sigma$ certainty. They show approximate degeneracies in the information gained from a survey if they are ``stretched''. When the information of ellipses with degeneracies in different directions is combined, the degeneracies are removed and the constraints typically becomes much better on the relevant parameters.}
    \label{fig:paramconstraintsall}
\end{figure}

\begin{figure}
    \centering
    \tiny
    \begin{tabular}{lrrrrr}
        \hline
         Par            &   CMB + Gal Powersp &   CMB + Gal Bisp &   CMB Power- + Bisp &   Gal Power- + Bisp &   CMB + Gal Power- + Bisp \\
        \hline
         $H_0$          &        5.3683958191 &     0.8819917551 &        0.1393060101 &        0.6113966629 &              0.1212982914 \\
         $\sigma_8$     &        0.0000000157 &     0.0000000157 &        0.0000000057 &        0.0000000099 &              0.0000000046 \\
         $\Omega_b h^2$ &        5.5823437092 &     3.3491075426 &        2.8087163845 &        3.9650003059 &              2.2514916319 \\
        \hline
        \end{tabular}
\caption{Same as table \ref{tab:paramconstraintsall}, except for a smaller selection of parameters well constrained by lensing.}
\label{tab:paramconstraintstight}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/param_constraints_tight.pdf}
    \caption{Same as \ref{fig:paramconstraintsall}, except showing constraints for a set of parameters that can be determined particularly accurately with weak lensing surveys. We chose Hubble's constant, $H_0$, baryonic + dark matter density, $\Omega_m$, and the root mean square density variation when the matter distribution is smoothed on a scale of 8 megaparsecs, commonly known as $\sigma_8$.}
    \label{fig:paramconstraintstight}
\end{figure}

@@

\printbibliography

@@

\begin{table}[h]
    \centering
    \begin{tabular}{lcc}
    \toprule
    Parameter & Fiducial value & Finite difference ($h$) \\
    \midrule
    $H$            & $67.4$               & fiducial\,$\times0.1$   \\
    $\Omega_b h^2$ & $0.0223$             & fiducial\,$\times0.2$   \\
    $\Omega_c h^2$ & $0.119$              & fiducial\,$\times0.005$ \\
    $n_s$          & $0.965$              & fiducial\,$\times0.02$ \\
    $A_s$          & $2.13\times10^{-9}$  & fiducial\,$\times0.15$   \\
    $m_\nu$        & $0.06$               & fiducial\,$\times0.15$   \\
    $w_0$          & $-1$                 & $0.06$                  \\
    \bottomrule
    \end{tabular}
    \caption{Fiducial cosmological parameters and their finite-difference steps}
    \label{tab:cosmo-params-diff}
\end{table}
